Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-11-03 Supplemental-Material-B-Annotated-Analysis.Rmd
AOT-M data cleaning done ✅

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
lib <- c(
  "rmarkdown",
  "knitr",
  "remedy",
  "bookdown",
  "brms",
  "psych",
  "ggplot2",
  "ggthemes",
  "haven",
  "RColorBrewer",
  "plotly",
  "gridExtra",
  "ggpattern",
  "lme4",
  "nlme",
  "jtools",
  "gtsummary",
  "sessioninfo",
  "tibble",
  "pander",
  "devtools",
  "mada",
  "data.table",
  "plyr",
  "dplyr",
  "tidyr",
  "Hmisc",
  "kableExtra",
  "papaja",
  "stringr",
  "stringi",
  "reshape2",
  "lubridate"
)
invisible(lapply(lib, library, character.only = TRUE))
rm(lib)

@@

@@

@@

```

```{r newVarsStudents}

>>>>

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
lib <- c(
  "rmarkdown",
  "knitr",
  "remedy",
  "bookdown",
  "brms",
  "psych",
  "ggplot2",
  "ggthemes",
  "haven",
  "RColorBrewer",
  "plotly",
  "gridExtra",
  "ggpattern",
  "lme4",
  "nlme",
  "jtools",
  "gtsummary",
  "sessioninfo",
  "tibble",
  "pander",
  "devtools",
  "mada",
  "data.table",
  "plyr",
  "dplyr",
  "tidyr",
  "Hmisc",
  "kableExtra",
  "papaja",
  "stringr",
  "stringi",
  "reshape2",
  "lubridate",
  "purrr"
)
invisible(lapply(lib, library, character.only = TRUE))
rm(lib)

@@

df <- df %>%
  mutate(
    NonDutchContact = replace_na(NonDutchNum, 0), # make second non-Dutch countable
    NonDutchContact = ifelse(NonDutchContact > 1, 1, 0) # recode (yes = 1 -> 1, no = 2 -> 0)
  ) %>%
  mutate(
    OutgroupInteraction = factor(
      InteractionDumDutch,
      levels = c(0, 1),
      labels = c("No", "Yes")
    ),
    NonOutgroupInteraction = factor(
      rowSums(select(., c(InteractionDumNonDutch, NonDutchContact)), na.rm = TRUE), # combine the two non-Dutch Q.,
      levels = c(0, 1),
      labels = c("No", "Yes")
    )
  )

@@

# Allport's Conditions
df %>%
  #filter(OutgroupInteraction == "Yes") %>%
  select(
    InteractionContextEqualStatus,
    KeyNeedShared,
    InteractionContextCooperative,
    InteractionContextvoluntary
  ) %>%
  pairs.panels.new

df %>%
  #filter(OutgroupInteraction == "Yes") %>%
  select(
    InteractionContextEqualStatus,
    KeyNeedShared,
    InteractionContextCooperative,
    InteractionContextvoluntary
  ) %>%
  psych::describe(., skew=F,ranges=T) %>%
  as.data.frame() %>%
  select(-vars) %>%
  kable(., caption = "Descriptives of Allport's Condition items") %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

iaWorkerAllport <- 
  df %>%
  #filter(OutgroupInteraction == "Yes") %>%
  select(
    InteractionContextEqualStatus,
    KeyNeedShared,
    InteractionContextCooperative,
    InteractionContextvoluntary
  )

sjPlot::tab_itemscale(iaWorkerAllport)

pca <- parameters::principal_components(iaWorkerAllport)
factor.groups <- parameters::closest_component(pca)

sjPlot::tab_itemscale(iaWorkerAllport, factor.groups)

ltm::cronbach.alpha(na.omit(iaWorkerAllport), CI = TRUE)

data <- 
  df %>%
  select(
    PID,
    TIDnum,
    InteractionContextEqualStatus,
    KeyNeedShared,
    InteractionContextCooperative,
    InteractionContextvoluntary
  ) %>%
  drop_na %>%
  melt(
    ., 
    id.vars = c("PID", "TIDnum")
  )

horst::nestedAlpha(item.level.1 = "value",
                   level.2      = "TIDnum",
                   level.3      = "PID",
                   data         = data)
rm(data)

iaWorkerAllportScale <- 
  iaWorkerAllport %>%
  Scale::Scale() %>%
  Scale::ItemAnalysis()

df$AllportsCondition <-
  scoreItems(
    keys = c(1, 1, 1, 1),
    items = df %>% select(
      InteractionContextEqualStatus,
      KeyNeedShared,
      InteractionContextCooperative,
      InteractionContextvoluntary
    ),
    min = 0,
    max = 100
  )$scores

as.data.frame(psych::describe(df$AllportsCondition, skew=T)) %>%
  mutate(vars = "Allport's Conditions Index") %>%
  kable(., caption = "Allport's Conditions: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

histogram(df$AllportsCondition)

@@

# -------------------------------------------------------------------------------------------------------------
#                                 Center Relevant Variables
# -------------------------------------------------------------------------------------------------------------
# divide into trait and state
medicalOutWithinBetween <-
  MlTraitState(
    data = df %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "Competence",
        "Autonomy",
        "Relatedness",
        "AllportsCondition",
        "AttitudesDutch",
        "qualityOverall"
      )
  )

df <-
  MlTraitState(
    data = df,
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "Competence",
        "Autonomy",
        "Relatedness",
        "AllportsCondition",
        "AttitudesDutch",
        "qualityOverall"
      )
  )

# store
dtMedical$full <- df
rm(df)

# Between participants contact frequency
medicalContactFreq <- 
  dtMedical$full %>%
  group_by(PID) %>%
  summarise(
    n = n(),
    SumContactNL = sum(InteractionDumDutch, na.rm = TRUE),
    PercContactNL = SumContactNL / n * 100,
    SumContactNLAll = sum(ContactNum[InteractionDumDutch == 1], na.rm = TRUE),
    AvAttitude = mean(AttitudesDutch, na.rm = TRUE),
    AvQuality = mean(qualityOverall, na.rm = TRUE)
  ) %>%
  mutate(
    WinSumContactNL = DescTools::Winsorize(SumContactNL),
    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
  )

# select a subset of IDs to display in plots
medicalPltIDs <-
  dtMedical$full %>%
  group_by(PID) %>%
  summarise(n = n()) %>%
  slice_max(n, n = 20) %>% # chose the 20 with the most number of measurements
  select(PID) %>%
  as.matrix %>%
  as.vector

# select a subset of IDs to display in plots (only outgroup interactions)
medicalOutPltIDs <-
  dtMedical$full %>%
  filter(OutgroupInteraction == "Yes") %>%
  group_by(PID) %>%
  summarise(n = n()) %>%
  slice_max(n, n = 20) %>% # chose the 20 with the most number of measurements
  select(PID) %>%
  as.matrix %>%
  as.vector
```
